\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-18 notes/2loopNLSM.tex
need to write intro -- here's everything else

@@

\section{Introduction}
\section{Background}
 To set the stage, it is worth distinguishing between the algebraic properties of functionally symmetric kinematics that satisfy color-kinematics globally, and some of the other constructions that appear in the literature.

In this work, we will consider three different types of cubic representations, that we define below: 
\be
\qquad\qquad \stackrel{\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}}{\text{Bifundamental}}\qquad\qquad \stackrel{\Acubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue}}{\text{Adjoint}}
\ee
In this review, we will present examples of this distinct kinematic representations that have appeared in the literature. Though from the get go, we stress that in this work we are interested in identifying the analog of adjoint representations of the kinematic numerators; those for which all legs are equally preferrenced by the functional dressing. The only non-trivial $S$-matrix in the literature that exhibits this property to all-loop order, is that of Zakharov-Mikhailov theory \cite{Zakharov:1973pp, Cheung:2022mix}. We will briefly review the perturbative construction of this theory below.

\subsection{Color-dual Amplitudes}

@@

Color-kinematics duality is a statement about amplitude integrands.
Ignoring factors of $i$ and the coupling constant, a generic $m$-point $L$-loop amplitude in a color-dual theory -- such as NLSM, YM, or bi-adjoint scalar theory -- can be written as
\be
\mathcal{A}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma n_\Gamma}{d_\Gamma} .
\ee
Here the spacetime dimension is $D$.
Even though the underlying theory may have quartic (or higher multiplicity) vertices, it is possible to multiply and divide by propagators so that the sum runs over only purely cubic graphs $\Gamma$.
Overcounting is removed by the internal symmetry factor $S_\Gamma$, which tracks the number of graph symmetries with external legs held fixed.
The color factor $c_\Gamma$ is the string of structure constants $f^{abc}$ associated with the graph $\Gamma$,\footnote{This paper is focused on theories with particles that transform in the adjoint.  However, the double copy can be applied to a far more diverse set of theories with particles that transform in the fundamental or more diverse representations, see for example \cite{Johansson:2017srf, Johansson2014zca, Johansson:2015oia, Johansson:2019dnu} \jm{I cited DF$^2$ and fundamental fermions. Is there anything else anyone wants to mention?}.}
the denominator $d_\Gamma$ is the product of propagators associated with the graph $\Gamma$, and the numerator $n_\Gamma$ is all of the remaining kinematic factors including dot products of momenta and polarization vectors.

@@

Once color-dual numerators $n_\Gamma$ have been found, they can be used to replace the color factors ($c_\Gamma \to n_\Gamma$) in a \emph{different} amplitude to produce the corresponding amplitude in the double-copy theory
\be
\tilde{\mathcal{A}}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma \tilde{n}_\Gamma}{d_\Gamma} ~~ \xrightarrow{(c_\Gamma \to n_\Gamma)} ~~ \mathcal{M}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{n_\Gamma \tilde{n}_\Gamma}{d_\Gamma}.
\ee
Importantly, the $\tilde{n}_\Gamma$ do not need to respect color-kinematics duality.
The prototypical example of the double-copy is that YM double copied with YM results in gravity where the gauge invariance of each separate gluon produces the diffeomorphism invariance of the graviton.
The double copy can be proven at tree level using the KLT relations but there is significant evidence that the double copy persists to all loop orders \cite{KLT, KiermaierTalk} \citepls{Any loop papers we want?}.

@@

\subsection{Color-dual Lagrangians}

BCJ loves $\mathcal{L} = \bar{F} F$.
How this connects to SDYM, NLSM.
You can do tree and 1-loop.
Why the bowtie is so important.

\subsection{Color-dual Bootstrap}
\label{sec:bootstrap}

Aside from a few special theories \citepls{}, color-dual integrands are constructed from an ansatz.
The four conditions we impose on an ansatz are summarized here and elaborated on below.\footnote{The four ansatz conditions are similar to those of Ref.~\cite{Bern:2015ooa} except that the authors demand that the numerators have the same loop power counting as Feynman gauge Feynman rules.  This is an additional assumption that is most emphatically not made here.}
\begin{enumerate}
\item \textbf{Locality}: Diagram numerators are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams.
  \item  \textbf{Color-kinematics duality}: The numerators obey the same Jacobi identities as the color factors.
This implicitly requires that the integrand is expressed in terms of purely cubic diagrams.
\item  \textbf{Graph symmetries}: The diagram numerators are only a function of the diagram's topology and labeling.  Furthermore, the diagram numerators are invariant under the automorphisms of the diagrams \emph{including signs that compensate for color-factor sign changes}.
\item  \textbf{Unitarity cuts}: The cuts of the ansatz must reproduce the physical unitarity cuts of the theory.
\end{enumerate}

@@

\section{One-loop cubic construction}
Here we'll describe the why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well. It has to do with how the vector state sum mixes with the four-point contact.

This is most easily seen by decomposing the Yang-Mill three-point interaction in terms of the following vertex in Lorenz gauge:
\be \label{YMSvert}
\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = (\varepsilon_1\varepsilon_2)(\varepsilon_3 k_1)
\ee
With this, the full vector interaction can be expressed as a sum over cyclic permutations:
\be
\cubic{hgrey0}{gluon}{}{gluon}{}{gluon}{}  =  \cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed} + \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} + \Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} +\text{h.c.}
\ee
The state-sum between two three-point gluon vertex yields the following expansion in terms of YZ-theory vertices:
\be
 \AcubicB{hgrey0}{gluon}{}{gluon}{}{gluon}{}{gluon}{} =  \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{fermion2}{} + 5 \text{ perms} + \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed}
\ee
where we have defined a new oriented vertex in terms of our scalar-vector building block of \ref{YMSvert},
\be
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} = \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} +\cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed}\,.
\ee
All the $(\epsilon\epsilon)^1$ diagram permutations are isolated to the cubic sector and together manifest color-kinematics duality. However, the exception of the last diagram which introduces a $(\epsilon\epsilon)^2$ factor, must conspire with the Yang-Mills contact to preserve the duality off-shell
\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed} = (s_{13}-s_{12}) \epsilon_{(12)} \epsilon_{(34)}
One was to resolve this is to introduce higher spin modes in order to accomodate the internal index contractions needed to recover the s-channal contract:
\AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{Bfield}{nhpRed}{}{nhpRed} = s_{12 }(\epsilon_{(13)} \epsilon_{(24)} - \epsilon_{(14)} \epsilon_{(23)})
While introducing succesively higher spin states to the NMHV Lagrangian constructed in \cite{Ben-Shahar:2022ixa} could in principle work at tree level, we will see that it is not consistent with what we find at general loop order. We will comment on this in \sect{}. For now, we will study how to construct one-loop integrands consistent with the color-kinematics by isolating the cubic sector of the state sum above. This is easily understood in terms of a polarization decomposition introduced by one of the authors \cite{Pavao:2022kog} that decomposes vector amplitudes in terms of building blocks that preserve partial amplitude relations. 
\subsection{Block Decomposition of Yang-Mills}
Describe how different orders in $\varepsilon_i\varepsilon_j$ in pure Yang-Mills captures different cubic and contact sectors of the theory. All the $D$-dimensional Lagnrangians above can be understood as selecting specific on shell states to isolate the cubic sector of Yang-Mills at a given loop order. Start with reducible amplitude block decomp from Ref. \cite{Pavao:2022kog}:
\begin{eBox}
\begin{equation}\label{eq:pureVecRABD}
A_{(\sigma)}^{\text{YM}} = \sum_{k=0}^{\lfloor |\sigma|/2\rfloor}\sum_{\rho \in S^{2|k}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\end{eBox}
By a simple mass-dimensioin argument, we know the tree-level cubic sector is simply:
A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
and likewise at one-loop:
A_{(\text{1-loop})}^{\text{cubic}} = \sum_{\rho \in S^{2|0}_{\sigma}}\epsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
We can select out both of these manifestly cubic sectors by selecting only $\epsilon^+\epsilon^+$ in light-cone gauge (i.e. SDYM) and one-minus at tree-level OR what $J$-theory and $YZ$-theory select with their on-shell states. Indeed, the $D$-dimensional description of $J$ theory is just the following blocks in the RABD expansion of Yang-Mills:
A(...,\bar{J}_k,...)_{\text{tree}} = \sum_{j\neq k}\Delta^{(jk)}_{\text{tree}}
and similarly so at one-loop:
A(...)_{\text{1-loop}} \equiv \Delta^{(\varnothing)}_{\text{1-loop}}
To recover NLSM at one-loop, we need to extract out the $D$-dependent part that corresponds to an internal $YY$-loop from extra-dimensional scalars:
\begin{eBox}
A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\epsilon\rightarrow k}
\end{eBox}
Why must we take the derivative with respect to $D$? After all, $J$-theory and $YZ$-theory both have well defined propagators for internal $\bar{J}J$ and $\bar{Z}Z$ propagators. However, as we noted in the previous section, all the $J$ and $Z$ states must be on-shell in order to produce NLSM amplitudes. Thus, the unitarity cuts of $J$ theory at one-loop will not produce NLSM amplitudes. However, the internal $YY$-loop is a valid forward limit, since as constructed YZ theory is valid for off-shell Y-particles, and thus they serve as a valid forward limit. We will construct these one-loop integrands below in the next section. 
\subsection{Semi-abelian Yang-Mills theory}
\begin{eBox}
\mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
\end{eBox}
where,
\bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a
\subsection{One-loop color-dual integrands}
\simplebox = g_{\text{YM}}^4 X(k_1,l_1)X(k_2,l_2)X(k_3,l_3)X(k_4,l_4)
\nGonScalar
Note from James:  I've explicitly checked the nice form of the 1-loop numerators at 4pt, 6pt, and 8pt.
\simplebox = (2 f_\pi^{-1})^4 (l_1 k_1)(l_2 k_2)(l_3 k_3)(l_4 k_4)
where we define sequential loop momenta on the $n$-gon as $l_{i+1}= l_i+k_i$. Given this, the $n$-gon permits a equivalent expression in terms of inverse propagators:
\simplebox =f_\pi^{-4} [12][23][34][41]
Where we have define the antisymmetric kinematic variable, $[LR] = l_i^L - l_R^2$
\subsection{Two-loop obstruction}

\section{Two-loop bootstrap}

@@

ZM theory is governed by the Lagrangian
\be
\label{eq:ZMLagrangian}
\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \epsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) .
\ee
The color-stripped Feynman rule for the vertex is simply $V(k_1, k_2, k_3) \propto \epsilon_{\mu\nu}k_1^\mu k_2^\nu$ where off-shell color-kinematics duality to all orders in perturbation theory simply follows from the Schouten identity.
Since the theory only has a cubic vertex and the theory has manifest off-shell color-kinematics duality, it is trivial to read off the color-dual numerator for any graph.
From the presence of the Levi-Civita tensor $\epsilon^{\mu\nu}$, the theory clearly resides in two spacetime dimensions where scattering is notoriously plagued by infrared regulation issues.
Every on-shell particle is either a right mover, with momentum proportional to $k_R^\mu \equiv (1,1)$, or a left mover, with momentum proportional to $k_L^\mu \equiv (1,-1)$.
On-shell ZM amplitudes naturally divide into sectors corresponding to the configuration of left and right movers, where the scattering in many sectors is rather subtle.
Only \emph{ordered} amplitudes can be defined unambiguously from the Feynman rules.
At 4pt, only the alternating sector is free of subtleties and the amplitude for this process vanishes.
In equations, $A[LRLR]=0$ where $R$ corresponds to a right mover and $L$ corresponds to a left mover.
In every other configuration of right and left movers, such as $A[RRRR]$, one of the internal propagators is incidentally on-shell since $k_R^2=k_L^2=0$.

>>>>

\usepackage{tikz-feynman}

\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
\usetikzlibrary{external}  
\immediate\write18{mkdir -p images}  %% Create `pgf-img` directory
\tikzexternalize[                     %% Activate externalization
 prefix=images/,                    %% Avoid cluttering the directory
 system call={                       %% Use lualatex in system call
    pdflatex \tikzexternalcheckshellescape -halt-on-error -shell-escape -interaction=batchmode -jobname="\image" "\texsource" || rm "\image.pdf"
 },
]

@@

\section{Introduction}
\section{Background}
To set the stage, in this section we will provide an overview of color-kinematics duality -- both the on-shell and off-shell construction. We then explicate our approach for constructing color-dual integrands in theories for which the off-shell kinematic algebra has not yet been identified, like Yang-Mills and NLSM. 
\subsection{Color-dual Amplitudes}

@@

Color-kinematics duality is a statement about the off-shell graphical simplicity that manifest redundancy in the on-shell observables of gauge and gravity theories. Ignoring factors of $i$ and the coupling constant, a generic $m$-point $L$-loop amplitude in a color-dual theory -- such as NLSM, YM, or bi-adjoint scalar theory -- can be written as
\be
\mathcal{A}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma n_\Gamma}{d_\Gamma} .
\ee
Here the spacetime dimension is $D$.
Even though the underlying theory may have quartic (or higher multiplicity) vertices, it is possible to multiply and divide by propagators so that the sum runs over only purely cubic graphs $\Gamma$.
Overcounting is removed by the internal symmetry factor $S_\Gamma$, which tracks the number of graph symmetries with external legs held fixed.
The color factor $c_\Gamma$ is the string of structure constants $f^{abc}$ associated with the graph $\Gamma$,\footnote{This paper is focused on theories with particles that transform in the adjoint.  However, the double copy can be applied to a far more diverse set of theories with particles that transform in the fundamental or more diverse representations, see for example \cite{Johansson:2017srf, Johansson2014zca, Johansson:2015oia, Johansson:2019dnu} ref[Ingrid+JJ, Aslan+JJ] \jm{I cited DF$^2$ and fundamental fermions. Is there anything else anyone wants to mention?}.}
the denominator $d_\Gamma$ is the product of propagators associated with the graph $\Gamma$, and the numerator $n_\Gamma$ is all of the remaining kinematic factors including dot products of momenta and polarization vectors.

@@

Once color-dual numerators $n_\Gamma$ have been found, they can be used to replace the color factors ($c_\Gamma \to n_\Gamma$) in a \emph{different} amplitude to produce the corresponding amplitude in the double-copy theory
\be\label{DCconstruction}
\tilde{\mathcal{A}}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma \tilde{n}_\Gamma}{d_\Gamma} ~~ \xrightarrow{(c_\Gamma \to n_\Gamma)} ~~ \mathcal{M}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{n_\Gamma \tilde{n}_\Gamma}{d_\Gamma}.
\ee
Importantly, the $\tilde{n}_\Gamma$ do not need to respect color-kinematics duality.
The prototypical example of the double-copy is that YM double copied with YM results in gravity where the gauge invariance of each separate gluon produces the diffeomorphism invariance of the graviton.
The double copy can be proven at tree level using the KLT relations but there is significant evidence that the double copy persists to all loop orders \cite{KLT, KiermaierTalk} \citepls{Any loop papers we want?}.

@@

\subsection{Color-dual Lagrangians}
While BCJ relations is an on-shell statement about the color-dual nature of scattering amplitudes, one might aspire to hard code color-kinematics duality by realizing an off-shell Lagrangian description of the theory. The double-copy construction of \ref{DCconstruction} would suggest a manifestly cubic Lagrangian of the form:
\be
\mathcal{L} = P_V^{ab}P_W^{ij}\mathcal{O}^a_i \Box \mathcal{O}^b_j +  V^{abc} W^{ijk}\mathcal{O}^a_i \mathcal{O}^b_j \mathcal{O}^c_k
\ee
where $V^{abc}$ and $W^{ijk}$ are cubic Feynman rules mixing field operators $\mathcal{O}^{a}_i$ indexed by quantum numbers $a$ and $i$. We have introduced $P_V^{ab}$ and $P_W^{ij}$ projection operators to encode non-local kinetic structure that could in principle participate in the construction. Should the off-shell Feynman rules of this cubic theory be antisymmetric and satisfy Jacobi identities on all internal edges,
\begin{align}
\textit{anti-symmetry}:& \quad{}_{a_1}\langle V^{a_2} \rangle_{a_3}+\text{cyc}(23)=0\,,
\\
\textit{Jacobi identity}:& \quad {}_{a_1}\langle V^{a_2} V^{a_3}\rangle_{a_4}+\text{cyc}(234)=0\,,
\end{align}
where 
\be
{}_{a_1}\langle V^{a_2}V^{a_3}\cdots V^{a_{n-1}} \rangle_{a_n} \equiv V^{a_1a_2b_1}V^{b_1a_3b_2}\cdots V^{b_{n-3} a_{n-2}a_n}\,.
\ee
This is a sufficient condition of the amplitudes to obey BCJ relations. Off-shell desciription of color-dual theories are rare, and only a few examples are available in the literature. Typically when one goes about construction color-dual theories directly from a set of cubic interactions, higher point Jacobi and antisymmetry constraints require introducing additional operators. See refs \cite{} for some recent examples. Indeed, as we'll show in \ref{cubic}, Yang-Mills requires introducing a cubic 2-form interaction in order to manifest the kinematic algebra just at four-point. Absent information about the kinematic algebra, one can make progress in the construction of loop-level color-dual amplitudes by employing a color-dual bootstrap. 
\subsection{Color-dual Bootstrap}
\label{sec:bootstrap}

Aside from a few special theories that permit an off-shell Lagrangian description \citepls{}, color-dual integrands are constructed from an ansatz. The four conditions we impose on an ansatz are summarized here and elaborated on below.\footnote{The four ansatz conditions are similar to those of Ref.~\cite{Bern:2015ooa} except that the authors demand that the numerators have the same loop power counting as Feynman gauge Feynman rules.  This is an additional assumption that is most emphatically not made here.}
\begin{enumerate}
\item \textbf{Locality}: Diagram numerators are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams.
  \item  \textbf{Color-kinematics duality}: The numerators obey the same Jacobi identities as the color factors.
This implicitly requires that the integrand is expressed in terms of purely cubic diagrams.
\item  \textbf{Graph symmetries}: The diagram numerators are only a function of the diagram's topology and labeling.  Furthermore, the diagram numerators are invariant under the automorphisms of the diagrams \emph{including signs that compensate for color-factor sign changes}.
\item  \textbf{Unitarity cuts}: The cuts of the ansatz must reproduce the physical unitarity cuts of the theory.
\end{enumerate}

@@

\section{One-loop cubic construction} \label{cubic}
Here we'll describe why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well. It has to do with how the vector state sum mixes with the four-point contact. Starting with the Yang-Mills Lagrangian,
\be
\mathcal{L}^{\text{YM}} = -\frac{1}{2}(\partial_\mu A_\nu)^2 + f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu + f^{abe}f^{ecd}A^a_\mu A^b_\nu  A^c_\mu A^d_\nu 
\ee
We can express the Yang-Mill three-point interaction in terms of the following vertex in Lorenz gauge:
\be
T^k_{ij} = (\varepsilon_i\varepsilon_j)(\varepsilon_k p_i)
\ee
This kinematic generator is anti-symmetric in $1\leftrightarrow 2$ exchange, and from it we can construct the full Lorenz gauge Yang-Mills vertex by summing over cyclic permutations:
\be
V^{(123)}_{\text{YM}} = T^3_{12} +\text{cyc}(123)
\ee
Contracting this with the vector state sum, we can see that the cubic Yang-Mills vertex does not alone satisfy the four-point Jacobi identity:
\be\label{cubicJac}
{}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4+\text{cyc}(234) = \varepsilon_{(12)}  \varepsilon_{(34)} (s_{13}-s_{23}) +\text{cyc}(234) \neq 0
\ee
where $ \varepsilon_{(ij)} =  \varepsilon_{i}\cdot  \varepsilon_{j}$. Of course, it is not hard to see that one can simply absorb the remaining terms into the definition of the four-point kinematic numerators:
\be
{}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4 = {}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4 + s_{12} (\varepsilon_{(13)}\varepsilon_{(24)}-\varepsilon_{(14)}\varepsilon_{(23)})
\ee
where $V_{\text{YM}+B}$ indicates the introduction of an additional two-form studied in \cite{Ben-Shahar:2022ixa} for constructing the NMHV Yang-Mills Lagrangian. 
\be
{}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4+\text{cyc}(234) =0
\ee
where the new cubic Lagrangian is of the form:
\be
\mathcal{L}^{\text{YM}+B} = -\frac{1}{2}(\partial_\mu A_\nu)^2 - B_{\mu\nu}\Box\tilde{B}_{\mu\nu}+ f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu+ f^{abc} (B_{\mu\nu}+\Box \tilde{B}_{\mu\nu})^a A^b_\mu A^c_\nu
\ee
Of course, higher multiplicity would require further redefinition of the three-point vertex to satisfy Jacobi identites on all internal edges. While introducing successively higher spin states could in principle work at tree level, we will see that it is not consistent with what we find at general loop order. We will comment on this in \sect{}. For now, we will study how to construct one-loop integrands consistent with the color-kinematics by isolating the cubic sector of the state sum above.

As one can see above, the Jacobi identity of \ref{cubicJac} fails only in terms with two factors of polarization dot products, $(\varepsilon\varepsilon)^2$. Whereas, if we restricted ourselves to just considering factors with a single polarization dot product, the jacobi identity of Yang-Mills would be satisfied \textit{off-shell} and in arbitrary spacetime dimensions:
\be
{}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4\big|^{(\varepsilon\varepsilon)^1}+\text{cyc}(234) =0
\ee
Thus for our approach at one-loop, we aim to build color-dual integrands directly from kinematic factors of this form. The organizational principle underlying this construction can be easily understood in terms of a polarization decomposition of vector amplitudes introduced by one of the authors \cite{Pavao:2022kog}, which we summarize briefly below. 
\subsection{Block Decomposition of Yang-Mills}
The $D$-dimensional Lagrangians of \ref{} can be understood as selecting specific on shell states to isolate the cubic sector of Yang-Mills at a given loop order. Start with reducible amplitude block decomp from Ref. \cite{Pavao:2022kog}:
\begin{equation}\label{eq:pureVecRABD}
A_{(\sigma)}^{\text{YM}} = \sum_{k=0}^{\lfloor |\sigma|/2\rfloor}\sum_{\rho \in S^{2|k}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\end{equation}
By a simple mass-dimensioin argument, we know the tree-level cubic sector must be at $\mathcal{O}((\varepsilon\varepsilon)^1)$:
\be
A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\ee
while at one-loop, the cubic sector corresponds to $\mathcal{O}((\varepsilon\varepsilon)^0)$ in polarization dot products:
\be
A_{(\text{1-loop})}^{\text{cubic}} = \sum_{\rho \in S^{2|0}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\ee
When decomposed in this way, in order for the full amplitude to be gauge invariant, the polarization stripped building blocks, must obey a set of Ward-Identities between different helicity sectors:
 \begin{equation}\label{eq:GIrelA}
\Delta_{(\sigma)}^{(\rho)}\Big|_{\epsilon_i\rightarrow k_i} =-
\sum_{j \in \rho^c} (k_i \varepsilon_j)\Delta_{(\sigma )}^{(\rho\cup (ij))} \,.
\end{equation}
With this in hand, we can construct a Lagrangian description of the of the cubic sector for Yang-Mills, and will demonstrate that the resulting amplitudes with manifestly color-dual Feynman rules are equivalent to both SDYM and NLSM through one-loop. 
\subsection{Semi-abelian Yang-Mills theory}
As we demonstrate above, if we include factors of $(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to keep the Yang-Mills four-point contact for color-kinematics duality to be restored on-shell. However, the contrapositive is also true -- if we get rid of the four-point Yang-Mills vertex, then we only need terms that contribute to the manifestly color-dual cubic sector of the theory.

We can achieve this construction by splitting the gauge group of the full Yang-Mills action from $G \rightarrow G_L \times G_R$, where the full non-abelian gauge symmetry is restored only when we identify $G_L = G_R$. However, if we break the left gauge group down to $G_L \rightarrow U(1)^{N^2}$, and take the right gauge group to $G_R \rightarrow U(N)$, then we are left with a semi-abelian theory that is gauge invariant in the preffered $U(1)$-directions. We call this manifestly color-dual theory, \textit{semi-abelian Yang-Mills},
\begin{eBox}
\be
\mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
\ee
\end{eBox}
where,
\be
\bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
\ee
\be
F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c
\ee
Here we can think of the abelian vector as a background field that sources on-shell $A_\mu$ currents. Indeed, as we describe in the Appendix \ref{}, semi-abelian Yang-Mills theory is at the heart of YZ-theory \cite{}, J-theory \cite{}, and self-dual Yang-Mills \cite{}. We can use the Ward identity of \ref{eq:GIrelA} to check that the amplitudes are indeed gauge invariant with the abelian polarizations are taken on-shell, $\bar{\varepsilon} \rightarrow k$.

We can select out both of these manifestly cubic sectors by selecting only $\varepsilon^+\varepsilon^+$ in light-cone gauge (i.e. SDYM) and one-minus at tree-level OR what $J$-theory and $YZ$-theory select with their on-shell states. Indeed, the $D$-dimensional description of $J$ theory is just the following blocks in the RABD expansion of Yang-Mills:
\be
A(...,\bar{A}_k,...)_{\text{tree}} = \sum_{j\neq k}\Delta^{(jk)}_{\text{tree}}
\ee
and similarly so at one-loop:
\be
A(...)_{\text{1-loop}} \equiv \Delta^{(\varnothing)}_{\text{1-loop}}
\ee
To recover NLSM at one-loop, we need to extract out the $D$-dependent part that corresponds to an internal $YY$-loop from extra-dimensional scalars:
\begin{eBox}
\be
A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\varepsilon\rightarrow k}
\ee
\end{eBox}
Why must we take the derivative with respect to $D$? After all, $J$-theory and $YZ$-theory both have well defined propagators for internal $\bar{J}J$ and $\bar{Z}Z$ propagators. However, as we noted in the previous section, all the $J$ and $Z$ states must be on-shell in order to produce NLSM amplitudes. Thus, the unitarity cuts of $J$ theory at one-loop will not produce NLSM amplitudes. However, the internal $YY$-loop is a valid forward limit, since as constructed YZ theory is valid for off-shell Y-particles, and thus they serve as a valid forward limit. We will construct these one-loop integrands below in the next section.

\subsection{One-loop color-dual integrands}
Our first application of this theory for color-dual construction at loop level is for self-dual Yang-Mills (SDYM). At tree-level, the off-shell cubic vertices can be written in terms of light cone coordinates \cite{}:
\be
X(p,k) = p_u k_w-p_w k_u
\ee
At loop-level, this construction needs to be analytically continued to general dimension in order to apply dimensional regularization at one-loop. This can be done using the cubic semi-YM vertices of the previous section:
\be
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\varepsilon_3)(\varepsilon_2 k_3) -  (\varepsilon_2\varepsilon_3)(\varepsilon_1 k_3)
\ee
Plugging in on-shell all-plus helicity states in light-cone gauge will yield precisely the 4D SDYM vertex, up to an unphysical phase. Of course, this has the advantage of permitting a $D$-dimensional construction of the one-loop integrand. Below we provide a four-point example:
\be
\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\mathcal{X}(k_3,l_3)\mathcal{X}(k_4,l_4)\rangle
\ee
where $l_i = l+k_1+k_2+\cdots+ k_i$. In general, the $n$-gon vertex would be
\be
\mathcal{N}^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\cdots \mathcal{X}(k_n,l_n) \rangle
\ee
Due to the state-sum of internal loop factors, $\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}=D$, the integrand above depends explicitly on the spacetime dimension, $D$. By taking a derivative, we can recover the integrand needed for all-plus one-loop amplitudes with an internal scalar:
\be
\ee
Note from James:  I've explicitly checked the nice form of the 1-loop numerators at 4pt, 6pt, and 8pt.
\be
\nGonScalar \equiv \frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}} = (2 g_{\text{YM}})^n (l_1 k_1)(l_2 k_2)\cdots (l_n k_n)
\ee
This integrand numerator with internal scalar loop is precisely what one would obtain from the Feynman rules of YZ-theory, absent the $XZ$ internal vector loop. For more background, we refer the reader to appendix \ref{}. 
\be
\left[\nGonScalar\right]_{\epsilon \rightarrow k} =  f_\pi^{-n} [12][23]\cdots [n1]
\ee
Where we have define the antisymmetric kinematic variable, $[LR] = l_L^2 - l_R^2$
\subsection{Two-loop obstruction}
At two-loop, introducing terms that conspire with four-point contacts is unavoidable. Thus, to approach the problem of two-loop construction, we employ an ansatz based approach. 
\section{Two-loop bootstrap}

@@

ZM theory is governed by the Lagrangian
\be
\label{eq:ZMLagrangian}
\mathcal{L}^{\text{ZM}} = \frac{1}{2}(\partial \varphi)^2 + g f^{abc} \varphi^a \varepsilon^{\mu\nu}(\partial_\mu \varphi^b)( \partial_\nu \varphi^c) .
\ee
The color-stripped Feynman rule for the vertex is simply $V(k_1, k_2, k_3) \propto \varepsilon_{\mu\nu}k_1^\mu k_2^\nu$ where off-shell color-kinematics duality to all orders in perturbation theory simply follows from the Schouten identity.
Since the theory only has a cubic vertex and the theory has manifest off-shell color-kinematics duality, it is trivial to read off the color-dual numerator for any graph.
From the presence of the Levi-Civita tensor $\varepsilon^{\mu\nu}$, the theory clearly resides in two spacetime dimensions where scattering is notoriously plagued by infrared regulation issues.
Every on-shell particle is either a right mover, with momentum proportional to $k_R^\mu \equiv (1,1)$, or a left mover, with momentum proportional to $k_L^\mu \equiv (1,-1)$.
On-shell ZM amplitudes naturally divide into sectors corresponding to the configuration of left and right movers, where the scattering in many sectors is rather subtle.
Only \emph{ordered} amplitudes can be defined unambiguously from the Feynman rules.
At 4pt, only the alternating sector is free of subtleties and the amplitude for this process vanishes.
In equations, $A[LRLR]=0$ where $R$ corresponds to a right mover and $L$ corresponds to a left mover.
In every other configuration of right and left movers, such as $A[RRRR]$, one of the internal propagators is incidentally on-shell since $k_R^2=k_L^2=0$.
